Temporal Graph Cube

### 2023-01-27 TemporalGraphCube/TemporalGraphCube_revision.tex
response 1-28

Using \kw{MinLevel}, we precompute views with small number of dimensions; and these views also have high similarity of snapshots in their snapshot arrays (as shown in Table~\ref{tab:materialized_view}). In processing temporal cuboid query $ Q=(A',[l,r]) $, if $ A' $ is not precomputed and $ l_0=1 $, only $ A_{base} $ can be used to process the query $ Q $. If $ l_0>1 $ and $ |dim(A')|<l_0 $, then there may be some precomputed views $ \{A_1'',A_2'',...\} $ where $ |dim(A_i'')|=l_0 $ can be used to process $ Q $. In this case, choosing an arbitrary $ A_i'' $ to process $ Q $ is efficient enough because the size of $ A_i'' $ and its index is usually small since $ l_0 $ is a small value.

@@

\subsection{Effectiveness Evaluation} \label{subsec:effectiveness_eva}
In this section, we evaluate the effectiveness of temporal graph cube as a decision-support tool on \kw{DBLP}. First, we conduct a series of temporal cuboid queries $ Q_1=((\kw{Area}),[2001,2006]) $, $ Q_2=((\kw{Area}),[2006,2011]) $, $ Q_3=((\kw{Area}),[2011,2016]) $, $ Q_4=((\kw{Area}),[2016,2021]) $ on \kw{DBLP}. Aggregation functions upon vertices and edges are both COUNT($\ast$). The network structures of $ Q_1 $-$ Q_4 $ are shown in Fig.~\ref{fig:dblp_area}, illustrating the co-authorship patterns between authors grouped by different areas in the specified time ranges. For simplicity, in Fig.~\ref{fig:dblp_area} (a) we omit those co-authorships with COUNT($\ast$) values less than 10,000, which are also omitted in Fig.~\ref{fig:dblp_area} (b)-(d), regardless of their COUNT($\ast$) values.

@@

\begin{figure*}[t!]
	\begin{center}
		\begin{tabular}[t]{c}\hspace*{-0.3cm}
			\subfigure[{\scriptsize $ Q_1 $}]{
				\includegraphics[width=0.23\textwidth]{fig/exp/visio_area_2001_2006.pdf}
			}
			\hspace*{-0.3cm}
			\subfigure[{\scriptsize $ Q_2 $}]{
				\includegraphics[width=0.23\textwidth]{fig/exp/visio_area_2006_2011.pdf}
			}
			\hspace*{-0.3cm}
			%\vspace*{-0.3cm}\\\hspace*{-0.3cm}
			\subfigure[{\scriptsize $ Q_3 $}]{
				\includegraphics[width=0.23\textwidth]{fig/exp/visio_area_2011_2016.pdf}
			}
			\hspace*{-0.3cm}
			\subfigure[{\scriptsize $ Q_4 $}]{
				\includegraphics[width=0.23\textwidth]{fig/exp/visio_area_2016_2021.pdf}
			}
		\end{tabular}
	\end{center}
	\vspace*{-0.4cm}
	\caption{Network structures in the results of queries $ Q_1-Q_4 $}
	\vspace*{-0.4cm}
	\label{fig:dblp_area}
\end{figure*}
\comment{
The results are shown in Table~\ref{tab:vertex_table_dblp_area} and Fig.~\ref{fig:dblp_area}. The network structures of $ Q_1 $-$ Q_4 $ are shown in Fig.~\ref{fig:dblp_area}, illustrating the co-authorship patterns between authors grouped by different areas in the specified time ranges. For simplicity, in Fig.~\ref{fig:dblp_area} (a) we omit those co-authorships with COUNT($\ast$) values less than 10,000, which are also omitted in Fig.~\ref{fig:dblp_area} (b)-(d), regardless of their COUNT($\ast$) values.
}

Some interesting observations can be obtained in these results. For example, authors in each area co-author most with authors in the same area even in different time ranges. We can clearly see that in recent 20 years, the number of co-authorship between each pair of areas increases over time. We can also find that in recent 20 years researchers in \kw{AI} co-authored with researchers in \kw{CG} most. This is because there are many problems in computer graphics like automatic modeling, image processing and digital photography which can be solved by AI technologies. More interestingly, in $ [2001,2006] $, researchers in \kw{TH} co-authored most with researchers in \kw{CA}, but with the time evolves, researchers in \kw{TH} are more willing to co-author with researchers in \kw{AI}. The reason may be that theoretical research on AI becomes more and more important with the wide applications of AI in recent years. %The above findings can also be obtained from uncut results.
%[ns and cn,ca and ai;ai and cg;th and ai,ca]

In each period we can zoom into a more fine-grained view by conducting a drill-down operation. For example, for $ Q_4=((\kw{Area}),[2016,2021]) $, drill-down can be a query $ Q_4'=((\kw{Area},\kw{Productivity}),[2016,2021]) $. The network structure of $ Q_4' $ is shown in Fig.~\ref{fig:dblp_area_pro_2016_2021}.
\begin{figure}
	\begin{center}
		\includegraphics[width=0.8\columnwidth]{fig/exp/visio_area_pro_2016_2021.pdf}
	\end{center}

	\vspace*{-0.6cm}
	\caption{Network structure in the result of $ Q_4' $}
	\vspace*{-0.4cm}
	\label{fig:dblp_area_pro_2016_2021}
\end{figure}
For simplicity, we drop edges with weight less than 10,000 and we only keep vertices related to areas in $ \{\kw{AI},\kw{DB}\} $ (it can be regarded as a slice-and-dice operation). In Fig.~\ref{fig:dblp_area} (d), there are 117,338 co-authorships between researchers of \kw{AI} and \kw{DB} in $ [2016,2021] $. In fine-grained view of Fig.~\ref{fig:dblp_area_pro_2016_2021}, we can see that the most co-authorships belong to researchers of poor and fair productivity in \kw{AI} and \kw{DB}.

We then examine the effectiveness of temporal crossboid query.
\begin{figure*}[t!]
	\begin{center}
		\begin{tabular}[t]{c}\hspace*{-0.3cm}
			\subfigure[{\scriptsize $ Q_{cross1} $}]{
				\includegraphics[width=0.25\textwidth]{fig/exp/dblp_cross_name_area_2001_2006.pdf}
			}
			\hspace*{-0.3cm}
			\subfigure[{\scriptsize $ Q_{cross2} $}]{
				\includegraphics[width=0.25\textwidth]{fig/exp/dblp_cross_name_area_2006_2011.pdf}
			}
			\hspace*{-0.3cm}
			%\vspace*{-0.3cm}\\\hspace*{-0.3cm}
			\subfigure[{\scriptsize $ Q_{cross3} $}]{
				\includegraphics[width=0.25\textwidth]{fig/exp/dblp_cross_name_area_2011_2016.pdf}
			}
			\hspace*{-0.3cm}
			\subfigure[{\scriptsize $ Q_{cross4} $}]{
				\includegraphics[width=0.25\textwidth]{fig/exp/dblp_cross_name_area_2016_2021.pdf}
			}
		\end{tabular}
	\end{center}
	\vspace*{-0.4cm}
	\caption{Network structures in the results of $ Q_{cross1}-Q_{cross4} $}
	\vspace*{-0.4cm}
	\label{fig:dblp_cross}
\end{figure*}
Fig.~\ref{fig:dblp_cross} shows the results of a series of temporal crossboid queries:
\begin{center}
	$ Q_{cross1}=((\kw{Name}),(\kw{Area}),[2001,2006]) $,\\$ Q_{cross2}=((\kw{Name}),(\kw{Area}),[2006,2011]) $,\\$ Q_{cross3}=((\kw{Name}),(\kw{Area}),[2011,2016]) $,\\$ Q_{cross4}=((\kw{Name}),(\kw{Area}),[2016,2021]) $.
\end{center}
The above queries focus on the cross interaction between \kw{Name} and \kw{Area}, i.e., the co-authorship with each area for each researcher. We further slice-and-dice the results on \kw{Name} to show the results related to ``Jiawei Han". We can find that in recent 20 years, Jiawei cooperated with researchers in \kw{DB} most. Meanwhile, in recent 10 years he has more and more cooperations with researchers in \kw{AI}, which can be ignored compared to cooperations with researchers in \kw{DB} in early 10 years.

>>>>

Using \kw{MinLevel}, we precompute views with small number of dimensions; and these views also have high similarity of snapshots in their snapshot arrays (as shown in Table~\ref{tab:materialized_view}). In processing temporal cuboid query $ Q=(A',[l,r]) $, if $ A' $ is not precomputed and $ l_0=1 $, only $ A_{base} $ can be used to process the query $ Q $. If $ l_0>1 $ and $ |dim(A')|<l_0 $, then there may be some precomputed views $ \{A_1'',A_2'',...\} $ where $ |dim(A_i'')|=l_0 $ can be used to process $ Q $. In this case, choosing an arbitrary $ A_i'' $ to process $ Q $ is efficient enough because the size of $ A_i'' $ and its index is usually small since $ l_0 $ is a small value.\todo{todo}

@@

\subsection{Effectiveness Evaluation} \label{subsec:effectiveness_eva}
In this section, we evaluate the effectiveness of temporal graph cube as a decision-support tool on \kw{DBLP}. First, \revision{we build temporal graph cube on \kw{DBLP} and} conduct a series of temporal cuboid queries $ Q_1=((\kw{Area}),[2001,2006]) $, $ Q_2=((\kw{Area}),[2006,2011]) $, $ Q_3=((\kw{Area}),[2011,2016]) $, $ Q_4=((\kw{Area}),[2016,2021]) $. \revision{We also build static graph cube on \kw{DBLP} and conduct a cuboid query $ Q_{static}=(\kw{Area}) $}. Aggregation functions upon vertices and edges are both COUNT($\ast$). The network structures of $ Q_1 $-$ Q_4 $ \revision{and $ Q_{static} $} are shown in Fig.~\ref{fig:dblp_area}, illustrating the co-authorship patterns between authors grouped by different areas. For simplicity, in Fig.~\ref{fig:dblp_area} (a) we omit those co-authorships with COUNT($\ast$) values less than $ 10,000 $, which are also omitted in Fig.~\ref{fig:dblp_area} (b)-(e), regardless of their COUNT($\ast$) values.

@@

\begin{figure*}[t!]
	\begin{center}
		\begin{tabular}[t]{c}\hspace*{-0.3cm}
			\subfigure[{\scriptsize $ Q_1 $}]{
				\includegraphics[width=0.19\textwidth]{fig/exp/visio_area_2001_2006.pdf}
			}
			\hspace*{-0.3cm}
			\subfigure[{\scriptsize $ Q_2 $}]{
				\includegraphics[width=0.19\textwidth]{fig/exp/visio_area_2006_2011.pdf}
			}
			\hspace*{-0.3cm}
			%\vspace*{-0.3cm}\\\hspace*{-0.3cm}
			\subfigure[{\scriptsize $ Q_3 $}]{
				\includegraphics[width=0.19\textwidth]{fig/exp/visio_area_2011_2016.pdf}
			}
			\hspace*{-0.3cm}
			\subfigure[{\scriptsize $ Q_4 $}]{
				\includegraphics[width=0.19\textwidth]{fig/exp/visio_area_2016_2021.pdf}
			}
			\hspace*{-0.3cm}
			\subfigure[{\scriptsize $ Q_{static} $}]{
				\includegraphics[width=0.19\textwidth]{fig/exp/visio_area_static.pdf}
			}
		\end{tabular}
	\end{center}
	\vspace*{-0.4cm}
	\caption{Network structures in the results of queries $ Q_1-Q_4 $ \revision{and $ Q_{static} $. $ Q_1=((\kw{Area}),[2001,2006]) $, $ Q_2=((\kw{Area}),[2006,2011]) $, $ Q_3=((\kw{Area}),[2011,2016]) $, $ Q_4=((\kw{Area}),[2016,2021]) $ are temporal cuboid queries, $ Q_{static}=(\kw{Area}) $ is a cuboid query in static graph cube}}
	\vspace*{-0.4cm}
	\label{fig:dblp_area}
\end{figure*}
\comment{
The results are shown in Table~\ref{tab:vertex_table_dblp_area} and Fig.~\ref{fig:dblp_area}. The network structures of $ Q_1 $-$ Q_4 $ are shown in Fig.~\ref{fig:dblp_area}, illustrating the co-authorship patterns between authors grouped by different areas in the specified time ranges. For simplicity, in Fig.~\ref{fig:dblp_area} (a) we omit those co-authorships with COUNT($\ast$) values less than 10,000, which are also omitted in Fig.~\ref{fig:dblp_area} (b)-(d), regardless of their COUNT($\ast$) values.
}

Some interesting observations can be obtained in these results. For example, authors in each area co-author most with authors in the same area \revision{all the time ($ Q_{static} $) and} in different time ranges \revision{($ Q_1-Q_4 $)}. We can clearly see that in recent 20 years (\revision{$ Q_1-Q_4 $}), the number of co-authorship between each pair of areas increases over time. \revision{However, such results can never be found in $ Q_{static} $}. \comment{We can also find that in recent 20 years researchers in \kw{AI} co-authored with researchers in \kw{CG} most. This is because there are many problems in computer graphics like automatic modeling, image processing and digital photography which can be solved by AI technologies.}More interestingly, in $ [2001,2006] $, researchers in \kw{TH} co-authored most with researchers in \kw{CA}, but with the time evolves, researchers in \kw{TH} are more willing to co-author with researchers in \kw{AI}. The reason may be that theoretical research on AI becomes more and more important with the wide applications of AI in recent years. \revision{However, in $ Q_{static} $ we can only know that researchers in \kw{TH} co-authored most with researchers in \kw{AI}, but ignore the trend above.} %The above findings can also be obtained from uncut results.
%[ns and cn,ca and ai;ai and cg;th and ai,ca]

In each time range of temporal cuboid queries we can zoom into a more fine-grained view by conducting a drill-down operation. For example, for $ Q_4=((\kw{Area}),[2016,2021]) $, drill-down can be a query $ Q_4'=((\kw{Area},\kw{Productivity}),[2016,2021]) $. The network structure of $ Q_4' $ is shown in Fig.~\ref{fig:dblp_area_pro_2016_2021}.
\begin{figure}
	\begin{center}
		\includegraphics[width=0.7\columnwidth]{fig/exp/visio_area_pro_2016_2021.pdf}
	\end{center}

	\vspace*{-0.6cm}
	\caption{Network structure in the result of $ Q_4'=((\kw{Area},\kw{Productivity}),[2016,2021]) $}
	\vspace*{-0.4cm}
	\label{fig:dblp_area_pro_2016_2021}
\end{figure}
For simplicity, we drop edges with weight less than 10,000 and we only keep vertices related to areas in $ \{\kw{AI},\kw{DB}\} $ (it can be regarded as a slice-and-dice operation). In Fig.~\ref{fig:dblp_area} (d), there are 117,338 co-authorships between researchers of \kw{AI} and \kw{DB} in $ [2016,2021] $. In fine-grained view of Fig.~\ref{fig:dblp_area_pro_2016_2021}, we can see that the most co-authorships belong to researchers of poor and fair productivity in \kw{AI} and \kw{DB}.

We then examine the effectiveness of temporal crossboid query.
\begin{figure*}[t!]
	\begin{center}
		\begin{tabular}[t]{c}\hspace*{-0.3cm}
			\subfigure[{\scriptsize $ Q_{cross1} $}]{
				\includegraphics[width=0.19\textwidth]{fig/exp/dblp_cross_name_area_2001_2006.pdf}
			}
			\hspace*{-0.3cm}
			\subfigure[{\scriptsize $ Q_{cross2} $}]{
				\includegraphics[width=0.19\textwidth]{fig/exp/dblp_cross_name_area_2006_2011.pdf}
			}
			\hspace*{-0.3cm}
			%\vspace*{-0.3cm}\\\hspace*{-0.3cm}
			\subfigure[{\scriptsize $ Q_{cross3} $}]{
				\includegraphics[width=0.19\textwidth]{fig/exp/dblp_cross_name_area_2011_2016.pdf}
			}
			\hspace*{-0.3cm}
			\subfigure[{\scriptsize $ Q_{cross4} $}]{
				\includegraphics[width=0.19\textwidth]{fig/exp/dblp_cross_name_area_2016_2021.pdf}
			}
			\hspace*{-0.3cm}
			\subfigure[{\scriptsize $ Q_{cross-static} $}]{
				\includegraphics[width=0.19\textwidth]{fig/exp/dblp_cross_name_area_static.pdf}
			}
		\end{tabular}
	\end{center}
	\vspace*{-0.4cm}
	\caption{Network structures in the results of $ Q_{cross1}-Q_{cross4} $ \revision{and $ Q_{cross-static} $}. \revision{$ Q_{cross1}=((\kw{Name}),(\kw{Area}),[2001,2006]) $, $ Q_{cross2}=((\kw{Name}),(\kw{Area}),[2006,2011]) $, $ Q_{cross3}=((\kw{Name}),(\kw{Area}),[2011,2016]) $, $ Q_{cross4}=((\kw{Name}),(\kw{Area}),[2016,2021]) $ are temporal crossboid queries, $ Q_{cross-static}=((\kw{Name}),(\kw{Area})) $ is a static crossboid query in static graph cube}}
	\vspace*{-0.4cm}
	\label{fig:dblp_cross}
\end{figure*}
Fig.~\ref{fig:dblp_cross} shows the results of a series of temporal crossboid queries:
\begin{center}
	$ Q_{cross1}=((\kw{Name}),(\kw{Area}),[2001,2006]) $,\\$ Q_{cross2}=((\kw{Name}),(\kw{Area}),[2006,2011]) $,\\$ Q_{cross3}=((\kw{Name}),(\kw{Area}),[2011,2016]) $,\\$ Q_{cross4}=((\kw{Name}),(\kw{Area}),[2016,2021]) $,
\end{center}
\revision{and a static crossboid query $ Q_{cross-static}=((\kw{Name}),(\kw{Area})) $.} Above queries focus on the cross interaction between \kw{Name} and \kw{Area}, i.e., the co-authorship with each area for each researcher. We further slice-and-dice the results on \kw{Name} to show the results related to ``Jiawei Han". We can find that in all the queries, Jiawei cooperated with researchers in \kw{DB} most. Meanwhile, in recent 10 years he has more and more cooperations with researchers in \kw{AI}, which can be ignored compared to cooperations with researchers in \kw{DB} in early 10 years. \revision{However, in static crossboid query $ Q_{cross-static} $ (Figure~\ref{fig:dblp_cross} (e)) we can only find that Jiawei cooperated with researchers in \kw{DB} most, but we ignore that the number of co-authorships between them is decreasing while Jiawei co-authored with researchers in \kw{AI} more and more frequently.}
